Supplemental Material for submission ``Do Objects in Real-World Images Have a Canonical Name?''

### 2019-05-18 papers/EMNLP2019/modeling.tex

\subsection{Experimental Setup}
\textbf{THIS IS VERY CRYPTIC}
\paragraph{Model}
We used \citeauthor{anderson2018updown}'s \citeyear{anderson2018updown} bottom-up attention model\footnote{The features code and data is available at \url{https://github.com/peteanderson80/bottom-up-attention}}. 
It uses Faster R-CNN in conjunction with the ResNet-101 CNN and was pretrained on object and attribute annotations from VisualGenome (after initialization with pretrained ImageNet model).
\iffalse
"To pretrain the bottom-up attention model, we first initialize Faster R-CNN with ResNet-101 pretrained for classification on ImageNet [35]. We then train on Visual
Genome [21] data. To aid the learning of good feature
representations, we add an additional training output for
predicting attribute classes (in addition to object classes).
To predict attributes for region i, we concatenate the mean
pooled convolutional feature vi with a learned embedding
of the ground-truth object class, and feed this into an additional output layer defining a softmax distribution over each
attribute class plus a ‘no attributes’ class.
The original Faster R-CNN multi-task loss function contains four components, defined over the classification and
bounding box regression outputs for both the RPN and the
final object class proposals respectively. We retain these
components and add an additional multi-class loss component to train the attribute predictor"
\fi

>>>>

Our findings in Sections~\ref{sec:analysis} and~\ref{sec:taxo} are cause to question the appropriateness of the standard evaluation procedure of object naming or  detection methods, in which models are compared against a single symbol. 
%
%Let us assume that we can define, for each instance, it's canonical name as the most frequently produced one. 
Specifically, the assumption that there exists a canonical name for individual objects (instances), cannot be made in general.
This was shown by the high standard deviation in terms of the relative frequency of an instance's top response (column \%top in Table~\ref{tab:agree}), as well as an average mismatch of $27\%$~between the instances' top response and their VG name (\mbox{top=VG}). 
Further, as discussed in Section~\ref{sec:taxo}, many name alternatives are not hierarchically related to the VG name. 
Hence, to distinguish automatically whether a predicted name is a true error (e.g.,\ XX) or actually a valid alternative to the given "ground truth" (e.g.,\ XX), simple methods, such as querying a taxonomic hierarchy, do not suffice. 
\cs{also distributional similarity? Remember that we looked into this for the checkpoint and did not find a clear similarity threshold/pattern}

\cs{TODO: Say something about type disagreements on class-level, after having written the results discussion.}

\cs{Ah, we still should have a comparison model with above argumentation :/.}

\textbf{TBC, after results discussion done}
\subsection{Experimental Setup}
\textbf{THIS IS VERY CRYPTIC}

\paragraph{Model}
We used \citeauthor{anderson2018updown}'s \citeyear{anderson2018updown} bottom-up attention model\footnote{The features code and data is available at \url{https://github.com/peteanderson80/bottom-up-attention}}. 
It uses Faster R-CNN in conjunction with the ResNet-101 CNN and was pretrained on object and attribute annotations from VisualGenome (after initialization with pretrained ImageNet model).
\iffalse
"To pretrain the bottom-up attention model, we first initialize Faster R-CNN with ResNet-101 pretrained for classification on ImageNet [35]. We then train on Visual
Genome [21] data. To aid the learning of good feature
representations, we add an additional training output for
predicting attribute classes (in addition to object classes).
To predict attributes for region i, we concatenate the mean
pooled convolutional feature vi with a learned embedding
of the ground-truth object class, and feed this into an additional output layer defining a softmax distribution over each
attribute class plus a ‘no attributes’ class.
The original Faster R-CNN multi-task loss function contains four components, defined over the classification and
bounding box regression outputs for both the RPN and the
final object class proposals respectively. We retain these
components and add an additional multi-class loss component to train the attribute predictor"
\fi
